R Notebook

### 2023-11-06 R_code/paper_analysis.Rmd
new changes to ML pipeline

```{r}
library(scales)
library(tidyverse)
library(caret)
library(ggpubr)
library(pROC)
```

```{r}
prefix = "/Users/noa/Workspace/bootstrap_repo/ML_pipeline"

@@

Choose specific program
```{r}
program = 'raxml'
if (program=='fasttree') {
    all_models_performance = fasttree_all_models_performance
    final_models_performance = fasttree_final_models_performance
    group_performance = fasttree_group_performance
    vi = fasttree_vi
    enriched_test = fasttree_enriched_test

} else if (program=='iqtree') {
    all_models_performance = iqtree_all_models_performance
    final_models_performance = iqtree_final_models_performance
    group_performance = iqtree_group_performance
    vi = fasttree_vi
    enriched_test = iqtree_enriched_test
} else if (program=='raxml') {
    all_models_performance = raxml_all_models_performance
    final_models_performance = raxml_final_models_performance
    group_performance = raxml_group_performance
    vi = fasttree_vi
    enriched_test = raxml_enriched_test
}
```

General performance
```{r}
final_models_performance  %>% filter (dataset=='test', metric_type=='all_data') %>% dplyr::select (analysis_type,name,balanced_accuracy_score, mcc)
```

```{r}

@@

>>>>

```{r}
library(scales)
library(tidyverse)
library(caret)
library(ggpubr)
library(pROC)
```
```{r}
validation_data_prefix = "/Users/noa/Workspace/bootstrap_results/validation_data"
fasttree_validation_data = read_tsv(paste(validation_data_prefix,"/simulations_df_fasttree.tsv", sep = ""))
raxml_validation_data = read_tsv(paste(validation_data_prefix,"/simulations_df_raxml.tsv", sep = ""))
iqtree_validation_data = read_tsv(paste(validation_data_prefix,"/simulations_df_iqtree.tsv", sep = ""))
```

```{r}
prefix = "/Users/noa/Workspace/ML_results"

@@

Choose specific program
```{r}
program = 'iqtree'
if (program=='fasttree') {
    all_models_performance = fasttree_all_models_performance
    final_models_performance = fasttree_final_models_performance
    group_performance = fasttree_group_performance
    vi = fasttree_vi
    enriched_test = fasttree_enriched_test
    validation_data = fasttree_validation_data

} else if (program=='iqtree') {
    all_models_performance = iqtree_all_models_performance
    final_models_performance = iqtree_final_models_performance
    group_performance = iqtree_group_performance
    vi = fasttree_vi
    enriched_test = iqtree_enriched_test
    validation_data = iqtree_validation_data
} else if (program=='raxml') {
    all_models_performance = raxml_all_models_performance
    final_models_performance = raxml_final_models_performance
    group_performance = raxml_group_performance
    vi = fasttree_vi
    enriched_test = raxml_enriched_test
    validation_data = raxml_validation_data
}
```

General performance
```{r}
final_models_performance  %>% filter (dataset=='test', metric_type=='all_data') %>% dplyr::select (analysis_type,name,balanced_accuracy_score, mcc, AUC)
```

@@

```
Validation_data
```{r}
validation_data %>% dplyr::select (boot_run_time, extraction_running_time,nni_ll_eval_running_time)
